Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-08-22 docs/paper/paper.Rmd
add section for visual comparison

There is some suggestion that this was partially driven by the ensemble forecasting having non-exponetial uncertainty, unlike many infectious disease forecasting models.

@@

### Definition

@@

### Summary statistics

@@

## Forecast evaluation

@@

- Forecast performance overview for the ensemble and surrogate.
- Forecast performance overview by forecast horizon. Highlight degrading performance with this impacting the surrogate model to a greater degree. 
- Discussion country level differences in performance and link to potential growth rate trends. 
- Discuss differences between countries with different numbers and kinds of submitted forecast models.

>>>>

There is some suggestion that this was partially driven by the ensemble forecasting having non-exponential uncertainty, unlike many infectious disease forecasting models.

@@

### Definition {-}

@@

### Summary statistics {-}

@@

@@

In our example set of locations, the absolute performance of the ensemble and the surrogate model was similar in all locations at short forecast horizons though varied by location.
Performance was most comparable in Slovakia but in the United Kingdom and Germany in particular the surrogate model outperformed visibly worse for some forecast dates (Figure \@ref(fig:vis-forecasts)).
For both the ensemble and the surrogate performance visibly decreased as the forecast horizon increased though the relative difference in performance between models was relatively stable across horizons.
In general in the study period the ensemble appeared to be liable to underpredict and the surrogate model appeared more likely to overpredict. 
Both models forecast large reductions in incidence in Poland during May that did not occur whilst only the ensemble forecast spuriously forecast similar large reductions in Germany during June.
In comparison to the ensemble model the surrogate model appeared less likely to place weight on infeasibly large reductions in incidence during periods of declining incidence but on other hand was more likely to forecast continuing increases in incidence (for example in Febuary in Slokavkia and Poland).
Italy and Germany, which had the highest number of submitted models of the example locations had little clear difference in performance between the ensemble and surrogate models compared to other example locations.
